%PUBLISHED VERSION

%\newcommand{\CLASSINPUTlefttextmargin}{10cm}
%\newcommand{\CLASSINPUTbottomtextmargin}{2cm}

\documentclass[12pt]{IEEEtran}

\setlength{\columnsep}{14mm}

%\usepackage[scaled]{helvet}
%\renewcommand\familydefault{\sfdefault} 
%\usepackage[T1]{fontenc}

\usepackage{makecell}
%\usepackage{natbib}
%\usepackage[style=authoryear-ibid,backend=biber]{biblatex}
%\usepackage[style=authoryear-ibid]{biblatex}
%\addbibresource{Schuller.bib}

%\usepackage[utf8]{inputenc}

%\bibliographystyle{jcs}
%acm, alpha, apalike, ieeetr
%abbrv, plain, siam, unsrt
%jcs
%[resume]

\begin{document}
\LARGE
\noindent
%\nocite{*}
\title{Dec Kolakowski}
\textbf{Dec Kolakowski}
%\renewcommand{\normalsize}{\fontsize{8}{9}\selectfont}
%\normalsize
\small
\\
\\
Github: dpwdec
\\
LinkedIn: dec-kolakowski
\\
Website: dpwdec.github.io
\\

\section*{About}

\noindent{I am a software developer, a TDD enthusiast and an evangelist for clean code. I graduated with a first class degree from Trinity College in Musical Composition. I spent ten years making games as a hobbyist and working in technology-driven art and animation projects. Through using code in these projects I discovered a love for programming and it’s expressive potential. In 2020 I made the decision to transition fully into software development by attending Makers academy.}

\section*{Skills}

\noindent{\textbf{JavaScript:} Vanilla JS, React, Node.js, Express, Cypress, Jest, Async Mongoose} \\[3pt]
\textbf{Rust:} Cargo, Test  \\[3pt]
\textbf{Python:} Unittest, Pipenv  \\[3pt]
\textbf{Ruby:} RSpec, Capybara, Rails, Sinatra  \\[3pt]
\noindent{\textbf{Testing:} TDD, BDD, Spec / AAA Test Patterns} \\[3pt]
\textbf{Databases:} SQL, MongoDB, PostgreSQL  \\[3pt]
\textbf{Web Development:} API creation, Full stack, Single Page Web Apps, HTML, CSS  \\[3pt]

\section*{Education}

\subsection*{Makers Academy (April 2020 to July 2020)}

\begin{itemize}
\item Fullstack web development
\item Effective remote working
\item Object oritened design
\item Agile methologies
\item Test driven development
\item Ruby, JavaScript, Python
\end{itemize}

\subsection*{Trinity College (September 2011 to June 2015) - First Class Honours}
\begin{itemize}
\item Musical Composition (Orchestral and Electro-acoustic)
\item Created or participated in a range of artistic cross-cultural and internal collaborative arts projects.
\item Created professional recordings and integrated technology with music
\end{itemize}

\vskip 1in

\section*{Projects}
\subsection*{GraphWFC.rs}
\noindent{A generalised graph based implementation of Maxim Gumin's Wave Function Collapse algorithm.} \\[5pt]
\textbf{Tech Stack:} Rust, Cargo, Rand

\subsection*{Re-Engage Charity Organiser Portal}
\noindent{A tool developed for the UK registered Re-Engage charity to facilitate volunteer co-ordinators.} \\[5pt]
\textbf{Tech Stack:} JavaScript, Node.js, MongoDB, Express, React, Google Maps API (Directions/Rendering), Lodash, Genetic Algorithms, Cypress, Jest

\subsection*{Maker's B'n'B}
\noindent{A group full stack clone of Air B'n'B.} \\
\textbf{Tech Stack:} Ruby, Sinatra, Sinatra-Flash, Bcrypt, Pony, RSpec, Capybara \\[3pt]

\section*{Interests}

\begin{itemize}
\item I am long time meditator. I have trained in Dzogchen and Pali traditions.
\item I run a collaborative music video club on discord in which a community music video lovers come together to experience cross cultural music
\item I play music regularly (Grade 8 in Baroque Recorder)
\item Yoga and running
\end{itemize}




%\cite{Schuller09-TI2b }

%\renewcommand{\normalsize}{\fontsize{8}{9}\selectfont}
%\scriptsize
%\let\oldbibliography\thebibliography
%\renewcommand{\thebibliography}[1]{%
%  \oldbibliography{#1}%
%  \setlength{\itemsep}{-3.0pt}%
%}

\newpage

%\scriptsize
%\tiny
%\tiny	             	\large
%\scriptsize	 	\Large
%\footnotesize	 	\LARGE
%\small	 	\huge
%\normalsize	 	\Huge

%\renewcommand\bibname{{PUBLICATIONS}}
  %\bibliographystyle{ieeetr}
%acm, alpha, apalike, ieeetr
%abbrv, plain, siam, unsrt

\end{document}