%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Dec Kolakowski} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{1777 Chestnut Pl Unit NT-2006} % Your address
\moveleft.5\hoffset\centerline{Denver, CO 80202}
\moveleft.5\hoffset\centerline{(770) 401-6678}
\moveleft.5\hoffset\centerline{jteppinette@jteppinette.com}
\moveleft.5\hoffset\centerline{https://jteppinette.com}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	Technology SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{ SKILLS} 

{\sl \textbf{JavaScript:}} Golang, Python, JavaScript, Java, Lua. \\
{\sl \textbf{Operations Technologies:}} Docker, Terraform, Jenkins, Ansible, Vagrant, Vault, Consul, Kafka, Redis, OpenSMTPD, Cgit. \\
{\sl \textbf{Web Backend Technologies:}} ModSecurity, Nginx, Gunicorn, Django, Elasticsearch, PostgreSQL. \\
{\sl \textbf{Third Party Integrations:}} S3, MailChimp, MailGun, Okta (SSO), PingFederate (SSO), Facebook, OpenLDAP (LDAP), FreeIPA (LDAP), OpenDirectory (LDAP) \\
{\sl \textbf{Web Frontend Technologies:}} VueJS, AngularJS, Leaflet, Bootstrap, SASS, C3, D3. \\
{\sl \textbf{Cloud Providers:}} Digital Ocean IaaS, GCE IaaS, Heroku PaaS, Internal Enterprise Cloud. \\
{\sl \textbf{Operating Systems:}} MacOS, Windows 10, GNU/Linux (Debian / CentOS), OpenBSD, AIX, Solaris, Teradata/HANA (Appliances). \\
{\sl \textbf{Embedded Engineering:}} JavaFX, Raspberry Pi, SQLite, ObjectDB, Arduino. \\
 
%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{EXPERIENCE}

{\sl Development Lead - Global Compute Security} \hfill October 2017 - Present \\
Apple Inc, Cupertino, CA
\begin{itemize}
\item Lead the development of a global security and compliance web-based software platform that enforces best security and compliance practices across roughly 100 thousand users and hundreds of thousands of compute systems.
\item Design, develop, and package a highly portable agent running on hundreds of thousands of systems which reports security and compliance statistics back to to a central system.
\item Operate a 1TB+ PostgreSQL instance.
\item Integrated software engineering standards into group daily practices.
\item Leveraged Ansible to assist in the maintenance of a global fleet of web application firewalls and load balancers.
\item Provided an additional layer of web application security via a global WAF (Web Application Firewall).
\end{itemize} 

{\sl Software Engineer} \hfill June 2015 - October 2017 \\
Ionic Security Inc, Atlanta, GA
\begin{itemize}
\item Developed and designed a large AngularJS web application.
\item Implemented and maintained multiple enterprise API authentication strategies in Golang and AngularJS.
\item Leveraged Golang's compiled nature to simplify deployments and decrease ops issues.
\item Developed and maintained the development environment used by front end software engineers.
\item Developed a distributed authentication and routing system for a SOA using Golang, Nginx, and Lua.
\item Integrated the Jenkins Continuous Integration(CI) systems into the existing deployment processes.
\item Implemented web application security standards defined by OWASP.
\end{itemize} 

{\sl Software Engineer} \hfill August 2013 - June 2015 \\
Georgia Tech Research Institute, Electronic Systems Laboratory, Atlanta, GA 
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Designed and developed Django/AngularJS software systems for the Department of Defense, Army, and Navy.
\item Presented software demos to Department of Defense derived clients.
\end{itemize}
 
{\sl Consultant, Owner} \hfill May 2014 - Present\\
JTE Technologies, Atlanta, GA
\begin{itemize} 
\item Designed and developed large Django/AngularJS and Golang/AngularJS software systems.
\item Setup continuous deployments for multiple projects of varying technologies through GitLab CI and Docker Swarm.
\item Provisioned and maintained multiple Docker Swarm clusters using Ansible and Terraform.
\end{itemize} 

%----------------------------------------------------------------------------------------

\end{resume}
\end{document}